Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
tidy

<!-- TODO: edge overlap can indicate if some associations are dependent on context -->
<!-- sufficient observations is essential for capturing reliable networ -->

<!-- TODO: caveat social scale could also be diff types of relationships but GPS but point to hmm -->

<!-- TODO add? each ordinal network layer consisted of avg 380 fixes * ID -->
<!-- -------------------------------------------------- -->

@@

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. In our case study, we integrate proximity based social networks
that inherently rely on animal collective movement, and, in general, we found
that movement is likely an important mechanism driving social network
connectivity within and between habitat types.

<!-- fixed array -->
Although multilayer animal social networks are relatively novel [@Silk_2018],
movement behaviour within multilayer networks has been considered. Spatial
networks are physical locations (nodes) which are connected in a network when
individuals move between said locations (edges). For example, spatial networks
were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
example, nodes represent locations within the array, *intralayer edges*
represent individual movement frequency, and *interlayer edges* represent
contact probability among individuals at a given node [@Mourier_2019]. Although
movement between fixed arrays is inherent, networks are not constructed based on
continuous measures of dyadic or collective movement [@Long_2014]. Our case
study builds on the work of Mourier et al. (2019) and explicitly integrates
continuous and simultaneous measures of animal movement through space and time
as layers of a multilayer social network.

@@

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. In our caribou case study, we
show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability.

Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

<!-- y -->
Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. In addition, recent technological
advances have lead to increased data complexity and resolution. Remotely sensed
imagery collected by modern satellites provide, for example, 10 m spatial
resolution optical imagery at a temporal revisit period of five days at the
equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
at a higher temporal resolution [@B_rger_2016]. Given this increased
availability of complex data, it is important to consider using a broad
continuum of scales to fully capture ecological processes, carefully select and
combine sources of data with different temporal and spatial scales, and
establish a clear link between scales of observation and meaningful biology.
<!-- y -->

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks which incorporated high resolution GPS telemetry data and spatial land cover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore, e.g., number of observations, sociality across space
and time, are ones that can be observed as has traditionally been done in
ethology. We highlight ways in which scale ought to be considered for both
observed and remotely-sensed data when building social networks. Furthermore,
GPS telemetry data provides a link between large scale landscape properties and
fine scale social interactions as animal movement occurs across the landscape,
and when taken into account with multiple individuals can indicate association
patterns. Thus, a layer incorporating relocation data could be a great boon
linking spatial and social layer in multilayer networks.

>>>>

@@

Social processes, movement decisions, and space use are inextricably linked and
multilayer networks represent a potential analytical framework for linking these
processes [@Mourier_2019]. Movement as a collective group can reduce per capita
predation risk via detection-dilution trade-offs and improve information
transfer about the quality or location of resources to other group members
[@Jolles_2019]. We integrate proximity based social networks
that inherently rely on animal collective movement, and, in general, we found
that movement is likely an important mechanism driving social network
connectivity within and between habitat types.

<!-- fixed array -->
Although multilayer animal social networks are relatively novel [@Silk_2018],
movement behaviour within multilayer networks has been considered. Spatial
networks are physical locations (nodes) which are connected in a network when
individuals move between said locations (edges). For example, spatial networks
were applied to monitor movement of sharks (*Carcharhinus amblyrhynchos* and
*Carcharhinus melanopterus*) between fixed location autonomous arrays. In this
example, nodes represent locations within the array, *intralayer edges*
represent individual movement frequency, and *interlayer edges* represent
contact probability among individuals at a given node [@Mourier_2019]. Although
movement between fixed arrays is inherent, networks are not constructed based on
continuous measures of dyadic or collective movement [@Long_2014]. Our
study builds on the work of Mourier et al. (2019) and explicitly integrates
continuous and simultaneous measures of animal movement through space and time
as layers of a multilayer social network.

@@

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the potential novel analyses that vary social, spatial,
and temporal scale within a multilayer framework. We
show that (1) multilayer social networks can be scale-dependent, and (2) the use of multilayer networks could be useful for
identifying habitat or season-specific social processes. Our analyses of social,
spatial, and temporal scales in a multilayer network framework highlight the potential
to identify scales at which different properties of layers within a multilayer
network show the most variability. Furthermore, we discuss the potential
integration of individual phenotypes and fitness, collective movement, and
habitat selection for future analyses considering spatial ecology using
multilayer networks.

Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. In addition, recent technological
advances have lead to increased data complexity and resolution. Remotely sensed
imagery collected by modern satellites provide, for example, 10 m spatial
resolution optical imagery at a temporal revisit period of five days at the
equator [@Drusch_2012]. Similarly, animal tracking devices have become smaller
allowing their deployement on a wider variety of organisms [@Wikelski_2007] and
at a higher temporal resolution [@B_rger_2016]. Given this increased
availability of complex data, it is important to consider using a broad
continuum of scales to fully capture ecological processes, carefully select and
combine sources of data with different temporal and spatial scales, and
establish a clear link between scales of observation and meaningful biology.

Multilayer networks are complicated in that they can incorporate data as varied
as social interactions, landscape features, and seasons, all of which exist at
different scales and units of measurement. Our analysis of caribou multilayer
networks which incorporated high resolution GPS telemetry data and spatial land cover
data is grounded in the context of observed animal social networks, as the
scales we chose to explore, e.g., number of observations, sociality across space
and time, are ones that can be observed as has <!-- edit-->traditionally been done in
ethology. We highlight ways in which scale ought to be considered for both
observed and remotely-sensed data when building social networks. GPS telemetry 
data provides a link between large scale landscape properties and
fine scale social interactions as animal movement occurs across the landscape,
and when taken into account with multiple individuals<!-- edit--> can indicate association
patterns. Thus, a layer incorporating relocation data could be a great boon
linking spatial and social layer in multilayer networks.
